\chapter{I Will Be Their God}

\begin{goals}
\goal Consider who God is, and consider how He is similar and different from man.
\goal Explore the different ways God has revealed himself to man.
\goal Think about ways to improve my perspective on who God is.
\end{goals}

\begin{bible}

\bve{Genesis}{(17:1-8)}
1 When Abram was ninety-nine years old the Lord appeared to Abram and said to him, ``I am God Almighty; walk before me, and be blameless, 2 that I may make my covenant between me and you, and may multiply you greatly.'' 3 Then Abram fell on his face. And God said to him, 4 ``Behold, my covenant is with you, and you shall be the father of a multitude of nations. 5 No longer shall your name be called Abram, but your name shall be Abraham, for I have made you the father of a multitude of nations. 6 I will make you exceedingly fruitful, and I will make you into nations, and kings shall come from you. 7 And I will establish my covenant between me and you and your offspring after you throughout their generations for an everlasting covenant, to be God to you and to your offspring after you. 8 And I will give to you and to your offspring after you the land of your sojournings, all the land of Canaan, for an everlasting possession, and I will be their God.'' 

\bv{Psalms}{(8:1-9)}
O Lord, our Lord, how majestic is your name in all the earth! You have set your glory above the heavens. 2 Out of the mouth of babies and infants, you have established strength because of your foes, to still the enemy and the avenger. 3 When I look at your heavens, the work of your fingers, the moon and the stars, which you have set in place, 4 what is man that you are mindful of him, and the son of man that you care for him? 5 Yet you have made him a little lower than the heavenly beings and crowned him with glory and honor. 6 You have given him dominion over the works of your hands; you have put all things under his feet, 7 all sheep and oxen, and also the beasts of the field, 8 the birds of the heavens, and the fish of the sea, whatever passes along the paths of the seas. 9 Lord, our Lord, how majestic is your name in all the earth!

\bv{Ecclesiastes}{(3:11)}
11 He has made everything appropriate in its time. He has also set eternity in their heart, yet so that man will not find out the work which God has done from the beginning even to the end.

\bv{Hebrews}{(1:1-2)}
1 Long ago, at many times and in many ways, God spoke to our fathers by the prophets, 2 but in these last days he has spoken to us by his Son, whom he appointed the heir of all things, through whom also he created the world.

\bv{Luke}{(4:1-13)}
1 And Jesus, full of the Holy Spirit, returned from the Jordan and was led by the Spirit in the wilderness 2 for forty days, being tempted by the devil. And he ate nothing during those days. And when they were ended, he was hungry. 3 The devil said to him, ``If you are the Son of God, command this stone to become bread.'' 4 And Jesus answered him, ``It is written, `Man shall not live by bread alone.' '' 5 And the devil took him up and showed him all the kingdoms of the world in a moment of time, 6 and said to him, ``To you I will give all this authority and their glory, for it has been delivered to me, and I give it to whom I will. 7 If you, then, will worship me, it will all be yours.'' 8 And Jesus answered him, ``It is written, ``'You shall worship the Lord your God, and him only shall you serve.' '' 9 And he took him to Jerusalem and set him on the pinnacle of the temple and said to him, ``If you are the Son of God, throw yourself down from here, 10 for it is written,``'He will command his angels concerning you, to guard you,' 11 and ``'On their hands they will bear you up, lest you strike your foot against a stone.' '' 12 And Jesus answered him, ``It is said, `You shall not put the Lord your God to the test.' '' 13 And when the devil had ended every temptation, he departed from him until an opportune time. 

\bv{Luke}{(14:25-27)}
25 And behold, a lawyer stood up to put him to the test, saying, ``Teacher, what shall I do to inherit eternal life?'' 26 He said to him, ``What is written in the Law? How do you read it?'' 27 And he answered, ``You shall love the Lord your God with all your heart and with all your soul and with all your strength and with all your mind, and your neighbor as yourself.'' 28 And he said to him, ``You have answered correctly; do this, and you will live.'' 

\end{bible}

\begin{discussion}
\dsubsec{Introduction}{900-905}{5}

This lesson is about who God is.

\bvs{Genesis}{(17:1-8)} God's first covenant with Abraham says that he will be his God.

\dsubsec{Who is God?}{905-915}{10}

	\bvs{Psalms}{(8:1-9)} It's amazing that God is is mindful of us.

\dsubsec{How we come to know about God}{915-925}{10}

	\bvs{Ecclesiastes}{(3:11)} Eternity in the heart of man

  \bvs{Hebrews}{(1:1-2)} Fathers by the prophets, today His son
	
	By extension His Word.

\dsubsec{What does that mean for me?}{925-940}{15}

	\bvs{Luke}{(4:1-13)} Having a God gives you an anchor. 
	
	\bvs{Luke}{(14:25-27)} Love God and you will live.

\dsubsec{Review}{940-945}{5}
\end{discussion}