\chapter{They Shall Be My People}

\begin{goals}
\goal Recognize that God wants a people who choose Him voluntarily
\goal Understand that God always provides for people to come to Him
\goal Appreciate how unique and special a Christian's relationship with God is
\end{goals}

\begin{bible}

\bve{Matthew}{(22:1-14)}

1 And again Jesus spoke to them in parables, saying, 2 ``The kingdom of heaven may be compared to a king who gave a wedding feast for his son, 3 and sent his servants to call those who were invited to the wedding feast, but they would not come. 4 Again he sent other servants, saying, `Tell those who are invited, ``See, I have prepared my dinner, my oxen and my fat calves have been slaughtered, and everything is ready. Come to the wedding feast.''\thinspace' 5 But they paid no attention and went off, one to his farm, another to his business, 6 while the rest seized his servants, treated them shamefully, and killed them. 7 The king was angry, and he sent his troops and destroyed those murderers and burned their city. 8 Then he said to his servants, `The wedding feast is ready, but those invited were not worthy. 9 Go therefore to the main roads and invite to the wedding feast as many as you find.' 10 And those servants went out into the roads and gathered all whom they found, both bad and good. So the wedding hall was filled with guests.

11 ``But when the king came in to look at the guests, he saw there a man who had no wedding garment. 12 And he said to him, `Friend, how did you get in here without a wedding garment?' And he was speechless. 13 Then the king said to the attendants, `Bind him hand and foot and cast him into the outer darkness. In that place there will be weeping and gnashing of teeth.' 14 For many are called, but few are chosen.''

\bve{Ezekiel}{(37:1-28)}

1 The hand of the Lord was upon me, and he brought me out in the Spirit of the Lord and set me down in the middle of the valley; it was full of bones. 2 And he led me around among them, and behold, there were very many on the surface of the valley, and behold, they were very dry. 3 And he said to me, ``Son of man, can these bones live?'' And I answered, ``O Lord God, you know.'' 4 Then he said to me, ``Prophesy over these bones, and say to them, O dry bones, hear the word of the Lord. 5 Thus says the Lord God to these bones: Behold, I will cause breath to enter you, and you shall live. 6 And I will lay sinews upon you, and will cause flesh to come upon you, and cover you with skin, and put breath in you, and you shall live, and you shall know that I am the Lord.''

7 So I prophesied as I was commanded. And as I prophesied, there was a sound, and behold, a rattling, and the bones came together, bone to its bone. 8 And I looked, and behold, there were sinews on them, and flesh had come upon them, and skin had covered them. But there was no breath in them. 9 Then he said to me, ``Prophesy to the breath; prophesy, son of man, and say to the breath, Thus says the Lord God: Come from the four winds, O breath, and breathe on these slain, that they may live.'' 10 So I prophesied as he commanded me, and the breath came into them, and they lived and stood on their feet, an exceedingly great army.

11 Then he said to me, ``Son of man, these bones are the whole house of Israel. Behold, they say, `Our bones are dried up, and our hope is lost; we are indeed cut off.' 12 Therefore prophesy, and say to them, Thus says the Lord God: Behold, I will open your graves and raise you from your graves, O my people. And I will bring you into the land of Israel. 13 And you shall know that I am the Lord, when I open your graves, and raise you from your graves, O my people. 14 And I will put my Spirit within you, and you shall live, and I will place you in your own land. Then you shall know that I am the Lord; I have spoken, and I will do it, declares the Lord.''

15 The word of the Lord came to me: 16 ``Son of man, take a stick and write on it, `For Judah, and the people of Israel associated with him'; then take another stick and write on it, `For Joseph (the stick of Ephraim) and all the house of Israel associated with him.' 17 And join them one to another into one stick, that they may become one in your hand. 18 And when your people say to you, `Will you not tell us what you mean by these?' 19 say to them, Thus says the Lord God: Behold, I am about to take the stick of Joseph (that is in the hand of Ephraim) and the tribes of Israel associated with him. And I will join with it the stick of Judah, and make them one stick, that they may be one in my hand. 20 When the sticks on which you write are in your hand before their eyes, 21 then say to them, Thus says the Lord God: Behold, I will take the people of Israel from the nations among which they have gone, and will gather them from all around, and bring them to their own land. 22 And I will make them one nation in the land, on the mountains of Israel. And one king shall be king over them all, and they shall be no longer two nations, and no longer divided into two kingdoms. 23 They shall not defile themselves anymore with their idols and their detestable things, or with any of their transgressions. But I will save them from all the backslidings in which they have sinned, and will cleanse them; and they shall be my people, and I will be their God.

24 ``My servant David shall be king over them, and they shall all have one shepherd. They shall walk in my rules and be careful to obey my statutes. 25 They shall dwell in the land that I gave to my servant Jacob, where your fathers lived. They and their children and their children's children shall dwell there forever, and David my servant shall be their prince forever. 26 I will make a covenant of peace with them. It shall be an everlasting covenant with them. And I will set them in their land and multiply them, and will set my sanctuary in their midst forevermore. 27 My dwelling place shall be with them, and I will be their God, and they shall be my people. 28 Then the nations will know that I am the Lord who sanctifies Israel, when my sanctuary is in their midst forevermore.'' 

\bve{Romans}{(8:12-17)}

12 So then, brothers, we are debtors, not to the flesh, to live according to the flesh. 13 For if you live according to the flesh you will die, but if by the Spirit you put to death the deeds of the body, you will live. 14 For all who are led by the Spirit of God are sons of God. 15 For you did not receive the spirit of slavery to fall back into fear, but you have received the Spirit of adoption as sons, by whom we cry, ``Abba! Father!'' 16 The Spirit himself bears witness with our spirit that we are children of God, 17 and if children, then heirs—heirs of God and fellow heirs with Christ, provided we suffer with him in order that we may also be glorified with him.

\bvh{Deuteronomy}{(10:12-22)}

12 ``And now, Israel, what does the Lord your God ask of you except to fear the Lord your God by walking in all His ways, to love Him, and to worship the Lord your God with all your heart and all your soul?  13 Keep the Lord's commands and statutes I am giving you today, for your own good.  14 The heavens, indeed the highest heavens, belong to the Lord your God, as does the earth and everything in it.  15 Yet the Lord was devoted to your fathers and loved them. He chose their descendants after them—He chose you out of all the peoples, as it is today.  16 Therefore, circumcise your hearts and don't be stiff-necked any longer.  17 For the Lord your God is the God of gods and Lord of lords, the great, mighty, and awesome God, showing no partiality and taking no bribe.  18 He executes justice for the fatherless and the widow, and loves the foreigner, giving him food and clothing.  19 You also must love the foreigner, since you were foreigners in the land of Egypt.  20 You are to fear Yahweh your God and worship Him. Remain faithful to Him and take oaths in His name.  21 He is your praise and He is your God, who has done for you these great and awesome works your eyes have seen.  22 Your fathers went down to Egypt, 70 people in all, and now the Lord your God has made you as numerous as the stars of the sky.''

\bvh{Romans}{(8:28-30)}

28 We know that all things work together for the good of those who love God: those who are called according to His purpose.  29 For those He foreknew He also predestined to be conformed to the image of His Son, so that He would be the firstborn among many brothers.  30 And those He predestined, He also called; and those He called, He also justified; and those He justified, He also glorified.

\bve{IPeter}{(2:9-10)}

9 But you are a chosen race, a royal priesthood, a holy nation, a people for his own possession, that you may proclaim the excellencies of him who called you out of darkness into his marvelous light. 10 Once you were not a people, but now you are God's people; once you had not received mercy, but now you have received mercy.

\end{bible}

\begin{discussion}
\dsubsec{Introduction}{900-905}{5}
The last lesson was about who God is.  This lesson is about what God wants.

\dsubsec{God wants a people who choose Him voluntarily}{905-915}{10}

\bvs{Matthew}{(22:1-14)} You can refuse the Lord's feast

\dsubsec{God always makes a way for his people}{915-925}{10}

Serpent will be crushed

Noah from last week

God brought the children of Israel out of Egypt

\bvs{Ezekiel}{(37:7-10)} Dry bones \& ``I will be their God.  They shall be my people''\\

\bvs{Romans}{(8:12-17)} God adopts us as sons.\\

\dsubsec{Adjusting perspective to view myself as a special people}{925-940}{15}
%We probably don't have a problem with this.  We already think we're the only ones going to heaven.

\bvs{Deuteronomy}{(10:12-22)} The Lord set aside Israel as a special people who love Him

\bvs{Romans}{(8:28-30)} The Lord predestined the type of people who would be his\\

\bvs{IPeter}{(2:9-10)} The Lord people are a chosen race and a royal priesthood

\dsubsec{Review}{940-945}{5}
\end{discussion}

\begin{questions}
\q Interpret the `Valley of Dry Bones' prophecy in Ezekiel 37.
\q What does it mean for God's chosen people to be `predestined' as in Romans 8:29-30?
\q List some of the benefits of being one of God's `chosen people'.
\q How would you answer a person who says, ``Why would God create people at all if some of them will end up in hell?''
\end{questions}