\chapter{My Covenant They Broke}

\begin{goals}
\goal Summarize how Israel rejected God's love under the Old Covenant
\goal Examine the consequences of rejecting God's love for Israel and for us
\goal Develop a plan to prevent falling away from God
\end{goals}

\begin{bible}

\bve{Hebrews}{(3:1-19)}

Therefore, holy brothers, you who share in a heavenly calling, consider Jesus, the apostle and high priest of our confession, 2 who was faithful to him who appointed him, just as Moses also was faithful in all God's house. 3 For Jesus has been counted worthy of more glory than Moses—as much more glory as the builder of a house has more honor than the house itself. 4 (For every house is built by someone, but the builder of all things is God.) 5 Now Moses was faithful in all God's house as a servant, to testify to the things that were to be spoken later, 6 but Christ is faithful over God's house as a son. And we are his house if indeed we hold fast our confidence and our boasting in our hope. 7 Therefore, as the Holy Spirit says, ``Today, if you hear his voice,8 do not harden your hearts as in the rebellion, on the day of testing in the wilderness, 9 where your fathers put me to the test and saw my works for forty years. 10 Therefore I was provoked with that generation, and said, `They always go astray in their heart; they have not known my ways.' 11 As I swore in my wrath, `They shall not enter my rest.' ''

12 Take care, brothers, lest there be in any of you an evil, unbelieving heart, leading you to fall away from the living God. 13 But exhort one another every day, as long as it is called ``today,'' that none of you may be hardened by the deceitfulness of sin. 14 For we have come to share in Christ, if indeed we hold our original confidence firm to the end. 15 As it is said, ``Today, if you hear his voice, do not harden your hearts as in the rebellion.'' 16 For who were those who heard and yet rebelled? Was it not all those who left Egypt led by Moses? 17 And with whom was he provoked for forty years? Was it not with those who sinned, whose bodies fell in the wilderness? 18 And to whom did he swear that they would not enter his rest, but to those who were disobedient? 19 So we see that they were unable to enter because of unbelief. 

\bvh{Romans}{(9:30-33)}

30 What should we say then? Gentiles, who did not pursue righteousness, have obtained righteousness—namely the righteousness that comes from faith. 31 But Israel, pursuing the law for righteousness, has not achieved the righteousness of the law. 32 Why is that? Because they did not pursue it by faith, but as if it were by works. They stumbled over the stumbling stone. 33 As it is written:
\begin{quote}
Look! I am putting a stone in Zion to stumble over
and a rock to trip over,
yet the one who believes on Him will not be put to shame.
\end{quote}

%TODO: It's probably not necessary to read this whole thing.
\bve{Leviticus}{(26:1-45)}

``You shall not make idols for yourselves or erect an image or pillar, and you shall not set up a figured stone in your land to bow down to it, for I am the Lord your God. 2 You shall keep my Sabbaths and reverence my sanctuary: I am the Lord.

3 ``If you walk in my statutes and observe my commandments and do them, 4 then I will give you your rains in their season, and the land shall yield its increase, and the trees of the field shall yield their fruit. 5 Your threshing shall last to the time of the grape harvest, and the grape harvest shall last to the time for sowing. And you shall eat your bread to the full and dwell in your land securely. 6 I will give peace in the land, and you shall lie down, and none shall make you afraid. And I will remove harmful beasts from the land, and the sword shall not go through your land. 7 You shall chase your enemies, and they shall fall before you by the sword. 8 Five of you shall chase a hundred, and a hundred of you shall chase ten thousand, and your enemies shall fall before you by the sword. 9 I will turn to you and make you fruitful and multiply you and will confirm my covenant with you. 10 You shall eat old store long kept, and you shall clear out the old to make way for the new. 11 I will make my dwelling among you, and my soul shall not abhor you. 12 And I will walk among you and will be your God, and you shall be my people. 13 I am the Lord your God, who brought you out of the land of Egypt, that you should not be their slaves. And I have broken the bars of your yoke and made you walk erect.

14 ``But if you will not listen to me and will not do all these commandments, 15 if you spurn my statutes, and if your soul abhors my rules, so that you will not do all my commandments, but break my covenant, 16 then I will do this to you: I will visit you with panic, with wasting disease and fever that consume the eyes and make the heart ache. And you shall sow your seed in vain, for your enemies shall eat it. 17 I will set my face against you, and you shall be struck down before your enemies. Those who hate you shall rule over you, and you shall flee when none pursues you. 18 And if in spite of this you will not listen to me, then I will discipline you again sevenfold for your sins, 19 and I will break the pride of your power, and I will make your heavens like iron and your earth like bronze. 20 And your strength shall be spent in vain, for your land shall not yield its increase, and the trees of the land shall not yield their fruit.

21 ``Then if you walk contrary to me and will not listen to me, I will continue striking you, sevenfold for your sins. 22 And I will let loose the wild beasts against you, which shall bereave you of your children and destroy your livestock and make you few in number, so that your roads shall be deserted.

23 ``And if by this discipline you are not turned to me but walk contrary to me, 24 then I also will walk contrary to you, and I myself will strike you sevenfold for your sins. 25 And I will bring a sword upon you, that shall execute vengeance for the covenant. And if you gather within your cities, I will send pestilence among you, and you shall be delivered into the hand of the enemy. 26 When I break your supply of bread, ten women shall bake your bread in a single oven and shall dole out your bread again by weight, and you shall eat and not be satisfied.

27 ``But if in spite of this you will not listen to me, but walk contrary to me, 28 then I will walk contrary to you in fury, and I myself will discipline you sevenfold for your sins. 29 You shall eat the flesh of your sons, and you shall eat the flesh of your daughters. 30 And I will destroy your high places and cut down your incense altars and cast your dead bodies upon the dead bodies of your idols, and my soul will abhor you. 31 And I will lay your cities waste and will make your sanctuaries desolate, and I will not smell your pleasing aromas. 32 And I myself will devastate the land, so that your enemies who settle in it shall be appalled at it. 33 And I will scatter you among the nations, and I will unsheathe the sword after you, and your land shall be a desolation, and your cities shall be a waste.

34 ``Then the land shall enjoy its Sabbaths as long as it lies desolate, while you are in your enemies' land; then the land shall rest, and enjoy its Sabbaths. 35 As long as it lies desolate it shall have rest, the rest that it did not have on your Sabbaths when you were dwelling in it. 36 And as for those of you who are left, I will send faintness into their hearts in the lands of their enemies. The sound of a driven leaf shall put them to flight, and they shall flee as one flees from the sword, and they shall fall when none pursues. 37 They shall stumble over one another, as if to escape a sword, though none pursues. And you shall have no power to stand before your enemies. 38 And you shall perish among the nations, and the land of your enemies shall eat you up. 39 And those of you who are left shall rot away in your enemies' lands because of their iniquity, and also because of the iniquities of their fathers they shall rot away like them.

40 ``But if they confess their iniquity and the iniquity of their fathers in their treachery that they committed against me, and also in walking contrary to me, 41 so that I walked contrary to them and brought them into the land of their enemies—if then their uncircumcised heart is humbled and they make amends for their iniquity, 42 then I will remember my covenant with Jacob, and I will remember my covenant with Isaac and my covenant with Abraham, and I will remember the land. 43 But the land shall be abandoned by them and enjoy its Sabbaths while it lies desolate without them, and they shall make amends for their iniquity, because they spurned my rules and their soul abhorred my statutes. 44 Yet for all that, when they are in the land of their enemies, I will not spurn them, neither will I abhor them so as to destroy them utterly and break my covenant with them, for I am the Lord their God. 45 But I will for their sake remember the covenant with their forefathers, whom I brought out of the land of Egypt in the sight of the nations, that I might be their God: I am the Lord.''
		
\end{bible}

\begin{discussion}

\dsubsec{Introduction}{900-905}{5}

\dsubsec{Summarize how Israel rejected God's love under the Old Covenant}{905-915}{10}

\bvs{Hebrews}{(3:1-19)} Israel hardened their hearts to God.  Don't harden yours.

\bvs{Romans}{(9:30-33)} Israel, as a nation,  didn't attain salvation through the Old Covenant because they did not pursue it by faith.

\dsubsec{Examine the consequences of rejecting God's love for Israel and for us}{915-925}{10}

\bvs{Leviticus}{(26:1-45)} Israel's consequences for rejecting God.
\dsubsec{Develop a plan to prevent falling away from God}{925-940}{15}

Go back to Hebrews 3 and Romans 9

\dsubsec{Review}{940-945}{5}
\end{discussion}

\begin{questions}
\q List some of the ways in which Israel rejected God from Hebrew 3 and Romans 9.
\q List some of the physical consequences Israel faced for rejecting God's love from Leviticus 26.
\q In what ways did the Israelites stumble over the cornerstone, Jesus?
\q From Hebrews 3, what should we do to prevent losing our relationship with God?
\end{questions}