\chapter{Behold The Days Are Coming}
\begin{goals}
\goal Know some prophecies from the Old Testament about the New Covenant
\goal Analyze how New Covenant prophesies set the expectations and hopes for the faithful of the Old Covenant
\goal Evaluate Bible prophecies that are not yet fulfilled, and the expectations and hopes they set for us6
\end{goals}
\begin{bible}

\bve{Genesis}{(22:15-19)}

15 And the angel of the Lord called to Abraham a second time from heaven 16 and said, ``By myself I have sworn, declares the Lord, because you have done this and have not withheld your son, your only son, 17 I will surely bless you, and I will surely multiply your offspring as the stars of heaven and as the sand that is on the seashore. And your offspring shall possess the gate of his enemies, 18 and in your offspring shall all the nations of the earth be blessed, because you have obeyed my voice.'' 19 So Abraham returned to his young men, and they arose and went together to Beersheba. And Abraham lived at Beersheba.

\bvh{Luke}{(2:22-40)}
22 And when the days of their purification according to the law of Moses were finished, they brought Him up to Jerusalem to present Him to the Lord 23 (just as it is written in the law of the Lord: Every firstborn male will be dedicated to the Lord) 24 and to offer a sacrifice (according to what is stated in the law of the Lord: a pair of turtledoves or two young pigeons).

25 There was a man in Jerusalem whose name was Simeon. This man was righteous and devout, looking forward to Israel's consolation, and the Holy Spirit was on him. 26 It had been revealed to him by the Holy Spirit that he would not see death before he saw the Lord's Messiah. 27 Guided by the Spirit, he entered the temple complex. When the parents brought in the child Jesus to perform for Him what was customary under the law, 28 Simeon took Him up in his arms, praised God, and said:
\begin{quote}
29 Now, Master, You can dismiss Your slave in peace, as You promised.
30 For my eyes have seen Your salvation.
31 You have prepared it in the presence of all peoples --
32 a light for revelation to the Gentiles and glory to Your people Israel.
\end{quote}
33 His father and mother were amazed at what was being said about Him. 34 Then Simeon blessed them and told His mother Mary: ``Indeed, this child is destined to cause the fall and rise of many in Israel and to be a sign that will be opposed— 35 and a sword will pierce your own soul—that the thoughts of many hearts may be revealed.''

36 There was also a prophetess, Anna, a daughter of Phanuel, of the tribe of Asher. She was well along in years, having lived with her husband seven years after her marriage, 37 and was a widow for 84 years. She did not leave the temple complex, serving God night and day with fasting and prayers. 38 At that very moment, she came up and began to thank God and to speak about Him to all who were looking forward to the redemption of Jerusalem.

39 When they had completed everything according to the law of the Lord, they returned to Galilee, to their own town of Nazareth. 40 The boy grew up and became strong, filled with wisdom, and God's grace was on Him.

\bvh{Romans}{(8:18-23)}

18 For I consider that the sufferings of this present time are not worth comparing with the glory that is going to be revealed to us. 19 For the creation eagerly waits with anticipation for God's sons to be revealed. 20 For the creation was subjected to futility--not willingly, but because of Him who subjected it--in the hope 21 that the creation itself will also be set free from the bondage of corruption into the glorious freedom of God's children. 22 For we know that the whole creation has been groaning together with labor pains until now. 23 And not only that, but we ourselves who have the Spirit as the firstfruits--we also groan within ourselves, eagerly waiting for adoption, the redemption of our bodies.

\end{bible}

\begin{discussion}

\dsubsec{Introduction}{900-905}{5}

\dsubsec{Know some prophecies from the Old Testament about the New Covenant}{905-915}{10}

\bvs{Genesis}{(22:15-19)} Land, nation, seed promises to Abraham 

Most of the prophecies are about Jesus.  No wonder they thought about a physical kingdom.  I'm going to have to think more on this.

\dsubsec{Analyze how New Covenant prophesies set the expectations and hopes for the faithful of the Old Covenant}{915-925}{10}

\bvs{Luke}{(2:22-40)} People who were expecting the coming of Christ

\dsubsec{Evaluate Bible prophecies that are not yet fulfilled, and the expectations and hopes they set for us}{925-940}{15}


\bvs{Romans}{(8:18-23)} Christians are still waiting for their coming glory.

\dsubsec{Review}{940-945}{5}
\end{discussion}

\begin{questions}
\q What is the relationship between Abraham's `seed' promise in Genesis 22:15-19 and the New Covenant prophecy in Jeremiah 31:31-34?
\q Compare the reaction of Anna and Simeon to Christ's coming to the reaction of the Pharisees later in Jesus' ministry.
\q Explain what Romans 8:19 means which it says that 'all creation' is waiting on God's sons to be revealed.
\q What are you looking forward to about Christ's second coming?
\end{questions}