\chapter{From the Least to the Greatest}

\begin{goals}
% worldy churches do a lot for improving the lives of their fellow man, but we don't do that.
\goal Review the separation that existing under the Old Law between God and His people 
\goal Appreciate the breadth of people that make up the New Testament church
\goal Propose godly ways we can enhance the inclusiveness of the Lord's church
\end{goals}

\begin{bible}

\bve{Hebrews}{(9:1-14)}
1 Now even the first covenant had regulations for worship and an earthly place of holiness. 2 For a tent was prepared, the first section, in which were the lampstand and the table and the bread of the Presence. It is called the Holy Place. 3 Behind the second curtain was a second section called the Most Holy Place, 4 having the golden altar of incense and the ark of the covenant covered on all sides with gold, in which was a golden urn holding the manna, and Aaron's staff that budded, and the tablets of the covenant. 5 Above it were the cherubim of glory overshadowing the mercy seat. Of these things we cannot now speak in detail.

6 These preparations having thus been made, the priests go regularly into the first section, performing their ritual duties, 7 but into the second only the high priest goes, and he but once a year, and not without taking blood, which he offers for himself and for the unintentional sins of the people. 8 By this the Holy Spirit indicates that the way into the holy places is not yet opened as long as the first section is still standing 9 (which is symbolic for the present age). According to this arrangement, gifts and sacrifices are offered that cannot perfect the conscience of the worshiper, 10 but deal only with food and drink and various washings, regulations for the body imposed until the time of reformation.

11 But when Christ appeared as a high priest of the good things that have come, then through the greater and more perfect tent (not made with hands, that is, not of this creation) 12 he entered once for all into the holy places, not by means of the blood of goats and calves but by means of his own blood, thus securing an eternal redemption. 13 For if the blood of goats and bulls, and the sprinkling of defiled persons with the ashes of a heifer, sanctify for the purification of the flesh, 14 how much more will the blood of Christ, who through the eternal Spirit offered himself without blemish to God, purify our conscience from dead works to serve the living God.

\bve{Ephesians}{(3:1-6)}
1 For this reason I, Paul, a prisoner for Christ Jesus on behalf of you Gentiles-- 2 assuming that you have heard of the stewardship of God's grace that was given to me for you, 3 how the mystery was made known to me by revelation, as I have written briefly. 4 When you read this, you can perceive my insight into the mystery of Christ, 5 which was not made known to the sons of men in other generations as it has now been revealed to his holy apostles and prophets by the Spirit. 6 This mystery is that the Gentiles are fellow heirs, members of the same body, and partakers of the promise in Christ Jesus through the gospel.

\bve{Matthew}{(20:1-16)}

1 ``For the kingdom of heaven is like a master of a house who went out early in the morning to hire laborers for his vineyard. 2 After agreeing with the laborers for a denarius a day, he sent them into his vineyard. 3 And going out about the third hour he saw others standing idle in the marketplace, 4 and to them he said, `You go into the vineyard too, and whatever is right I will give you.' 5 So they went. Going out again about the sixth hour and the ninth hour, he did the same. 6 And about the eleventh hour he went out and found others standing. And he said to them, `Why do you stand here idle all day?' 7 They said to him, `Because no one has hired us.' He said to them, `You go into the vineyard too.' 8 And when evening came, the owner of the vineyard said to his foreman, `Call the laborers and pay them their wages, beginning with the last, up to the first.' 9 And when those hired about the eleventh hour came, each of them received a denarius. 10 Now when those hired first came, they thought they would receive more, but each of them also received a denarius. 11 And on receiving it they grumbled at the master of the house, 12 saying, `These last worked only one hour, and you have made them equal to us who have borne the burden of the day and the scorching heat.' 13 But he replied to one of them, `Friend, I am doing you no wrong. Did you not agree with me for a denarius? 14 Take what belongs to you and go. I choose to give to this last worker as I give to you. 15 Am I not allowed to do what I choose with what belongs to me? Or do you begrudge my generosity?' 16 So the last will be first, and the first last.''

\bvh{Ephesians}{(4:1-16)}
1 Therefore I, the prisoner for the Lord, urge you to walk worthy of the calling you have received, 2 with all humility and gentleness, with patience, accepting one another in love, 3 diligently keeping the unity of the Spirit with the peace that binds us. 4 There is one body and one Spirit--just as you were called to one hope at your calling-- 5 one Lord, one faith, one baptism, 6 one God and Father of all, who is above all and through all and in all.

7 Now grace was given to each one of us according to the measure of the Messiah's gift. 8 For it says:
\begin{quote}
When He ascended on high,
He took prisoners into captivity;
He gave gifts to people.
\end{quote}
9 But what does ``He ascended'' mean except that He descended to the lower parts of the earth? 10 The One who descended is also the One who ascended far above all the heavens, that He might fill all things. 11 And He personally gave some to be apostles, some prophets, some evangelists, some pastors and teachers, 12 for the training of the saints in the work of ministry, to build up the body of Christ, 13 until we all reach unity in the faith and in the knowledge of God's Son, growing into a mature man with a stature measured by Christ's fullness. 14 Then we will no longer be little children, tossed by the waves and blown around by every wind of teaching, by human cunning with cleverness in the techniques of deceit. 15 But speaking the truth in love, let us grow in every way into Him who is the head--Christ. 16 From Him the whole body, fitted and knit together by every supporting ligament, promotes the growth of the body for building up itself in love by the proper working of each individual part.

\bvh{James}{(2:1-7)}
My brothers, do not show favoritism as you hold on to the faith in our glorious Lord Jesus Christ. 2 For example, a man comes into your meeting wearing a gold ring and dressed in fine clothes, and a poor man dressed in dirty clothes also comes in. 3 If you look with favor on the man wearing the fine clothes and say, ``Sit here in a good place,'' and yet you say to the poor man, ``Stand over there,'' or, ``Sit here on the floor by my footstool,'' 4 haven't you discriminated among yourselves and become judges with evil thoughts?

5 Listen, my dear brothers: Didn't God choose the poor in this world to be rich in faith and heirs of the kingdom that He has promised to those who love Him? 6 Yet you dishonored that poor man. Don't the rich oppress you and drag you into the courts? 7 Don't they blaspheme the noble name that was pronounced over you at your baptism?

\end{bible}

\begin{discussion}
\dsubsec{Introduction}{900-905}{5}

\dsubsec{Review the separation that existing under the Old Law between God and His people }{905-915}{10}

\bvs{Hebrews}{(9:1-14)} The tabernacle separated the Israelites from God.

\bvs{Ephesians}{(3:1-6)} The mystery of the Gospel is that Gentiles can enter heaven.

\dsubsec{Appreciate the breadth of people that make up the New Testament church}{915-925}{10}

\bvs{Matthew}{(20:1-16)} Early or late

Corinthians not many wise.

\dsubsec{Propose godly ways we can enhance the inclusiveness of the Lord's church}{925-940}{15}

\bvs{Ephesians}{(4:1-16)} Christians are each part of a body, and work toward unity.

\bvs{James}{(2:1-7)} The church is made up of both rich and poor

\dsubsec{Review}{940-945}{5}
\end{discussion}

\begin{questions}
\q What is the mystery of the Gospel?
\q List some of the different types of people that could conflict with each other, but who must get along in the church (for example, rich and poor).
\q Paul lists some of the specific teaching roles that Ephesian Christians held (apostles, prophets, evangelists, pastors and teachers), but there are other areas where Christians may have personal strengths that are helpful to the body of Christ.  List as many as you can think of.
\q What areas could we improve on to increase the inclusiveness of the Lord's church?
\end{questions}