\clearpage
\section*{Scripture Reference}

\begin{scriptref}
\toprule
\multicolumn{3}{l}{\large Old Testament}\\
\endfirsthead
Passage & Ls. & Message \\
\midrule
\endhead
Gen. 2:20-24    & 5  & Husband and wife relationship is a very close bond\\
Gen. 6:17-18    & 4  & God made a covenant with Noah \\
Gen. 22:15-19   & 7  & Land, nation, seed promises to Abraham\\
Gen. 17:1-8     & 2  & ``I will be your God'' to Abraham\\
Ex. 6:1-9       & 1  & ``I will be your God'' to the Israelites\\
Lev. 22:31-33   & 1  & ``I am holy'', ``I am your God'', to the Israelites\\
Lev. 26:1-45    & 6  & Israel's consequences for rejecting God\\
Deut. 10:12-22  & 3  & The Lord set aside a special people whos' hearts are His\\
I Sam. 16:7     & 9  & Man looks at the outward appearance.  God looks at the heart.\\
Ezra 7:10       & 9  & Ezra chose what His heart would be like.\\
Psalm 8:1-9     & 2  & What is man that You are mindful of him?\\
Eccl. 3:11      & 2  & We know God because He set eternity in our heart\\
Jer. 31:31-34   & 1  & Prophecy of the New Covenant\\
Ezek. 37:1-28   & 3  & Dry bones \& ``I will be their God.  They shall be my people''\\
\bottomrule
\end{scriptref}
\clearpage
\begin{scriptref}
\toprule
\multicolumn{3}{l}{\large New Testament}\\
Passage & Ls. & Message \\
\midrule
\endhead
Matt. 7:7-12    & 10 & Keep asking and it will be given you.\\
Matt. 20:1-16   & 11 & Whether you come to God early or late, the reward is fixed.\\
Matt. 22:1-14   & 3  & You can refuse the Lord's offer of a relationship\\
Luke 2:22-40    & 7  & Simeon and Anna, two Israelites, were expecting Jesus\\
Luke 4:1-13     & 2  & Jesus rebuffs Satan by using God as His moral anchor\\
Luke 14:25-27   & 2  & Loving God is the key to eternal life\\
Luke 22:14-23   & 8  & Jesus' blood is the seal of the New Covenant\\
John 3:16       & 1  & God's love is His motivation for our salvation\\
Rom. 3:5-31     & 12 & Everyone is under sin, so that God may have mercy on all.\\
Rom. 4:1-25     & 10 & Those who have the faith of Abraham are his children.\\
Rom. 7:1-25     & 12 & Paul illustrates the impossibility perfect law keeping.\\
Rom. 8:1-11     & 12 & There is no condemnation of sin for those in Christ Jesus.\\
Rom. 8:12-17    & 3  & God adopts us as sons.\\
Rom. 8:18-23    & 7  & Christians are still waiting for their coming glory.\\
Rom. 8:28-30    & 3  & The Lord predestined the type of people who would be his\\
Rom. 9:30-33    & 6  & Israel didn't have faith and, so, stumbled over Jesus.\\
Rom. 11:25-32   & 8  & God shut everyone up under sin, so He can show mercy.\\
Rom. 12:1-2     & 9  & Christians commit to a total life transformation.\\
II Cor. 3:7-18  & 8  & The temple veil has been removed.  So we know God directly.\\
II Cor. 4:16-18 & 9  & The outer person fades, but the inner person is renewed.\\
Gal. 3:1-29     & 4  & Faith is the foundation of God's covenants\\
Eph. 2:1-21     & 8  & Jews and Gentiles are reconciled to God through Christ.\\
Eph. 3:1-6      & 11 & The mystery of the Gospel is that Gentiles can enter heaven.\\
Eph. 3:14-18    & 10 & Our heart is strengthened as we grow in knowing God's love.\\
Eph. 4:1-16     & 11 & Christians are each part of a body, and work toward unity.\\
Phil. 3:3-10    & 10 & We are the true circumcision, and we focus on knowing Christ.\\
Heb. 1:1-2      & 2  & We know God because He spoke by the prophets and His Son\\
Heb. 3:1-19     & 6  & Israel hardened their hearts to God.  Don't harden yours.\\
Heb. 4:1-13     & 9  & Don't have the Israel's heart, rather faith guided by the Word.\\
Heb. 8:1-13     & 1  &  The Old Covenant had faults and is replaced with the New\\
Heb. 9:1-14     & 11 & Jesus entered a spiritual Holy Place to bring true redemption.\\
Heb. 9:15-28    & 12 & Jesus is the solution to the problem of sin.\\
Heb. 10:1-23    & 8  & Jesus' sacrifice forgives and sanctifies, once for all.\\
Heb. 12:1-29    & 5  & God's discipline and the greatness of his plan motivates us\\
James 2:1-7     & 11 & The church has both rich and poor and they should get along.\\
I Pet. 2:9-10   & 3  & The Lord's people are a chosen race and a royal priesthood\\
I John 4:7-12   & 5  & Love is the main characteristic of God \ldots and Christians\\
I John 3:19-24  & 9  & A heart that has love and obedience gives us confidence.\\
\bottomrule
\end{scriptref}